Response to the defense feedback

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Step 1: Fuzzing}
After we build the software into the binary executable, we give the
binary code the random inputs. For cryptography libraries, the input
is the encryption key. For non-cryptography libraries, the input could
be images, text, and information in another format. Encryption
algorithms like AES and DES take an array representing the secrets. We
generate the random input by flipping each bit of the keys. Some other
programs also take a buffer as the input. The buffer may contain the
redundancy information and follow a specific format. So not any input
that satisfies the input length is a valid input. Under the
circumstance, we have a dictionary that contains the input. For
example, crypto libraries usually take PKCS \#1 as the input of the
RSA private key. We use some other tools to generate a list of valid
keys and use the key to sample the program. Due to the enormous search
space, we cannot iterate every input. However, our method can give a
conservative estimate of each leakage site.
\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by the AFL and Valgrind, we use the bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset (Load Memory Address (LMA)) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the enclave code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the enclave image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

>>>>

\subsection{Step 1: Fuzzing}
After we build the software into the binary executable, we give the
binary executable random inputs. For cryptography libraries, the input
is the encryption key. For non-cryptography libraries, the input could
be images, text, and information in another format. Encryption
algorithms like AES and DES take an array representing the secrets. We
generate the random input by flipping each bit of the keys. Some other
programs also take a buffer as the input. The buffer may contain 
redundancy information and follow a specific format. So not any input
that satisfies the input length is a valid input. Under the
circumstance, we have a dictionary that contains the input. For
example, crypto libraries usually take PKCS \#1 as the input of the
RSA private key. We use some other tools to generate a list of valid
keys and use the key to sample the program. Due to the enormous search
space, we cannot iterate every input. However, our method can give a
conservative estimate of each leakage site.
\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by the AFL and Valgrind, we use the bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset (Load Memory Address (LMA)) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the enclave code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the enclave image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.
